Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
...

@@

	\subsubsection{Simulations}
		gap of theoretical density with density in simulations : under $1$ percent, see Figure \ref{densiteth}

>>>>

	The network is a symmetric matrix with null diagonal and can therefore be stored in memory as $\frac{c(c-1) l^2}{2}$ bits. Since messages are not stored in an ordered fashion, the information stored is the set of messages, thereby it amounts to $\log_2(\frac{({l \choose a}^c)^m}{m!}) \approx m(c \log_2{l \choose a } - \log_2(m) + 1) $. The information effectively stored in the network is $P_{retrieve} \times m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2}$.

	Ambiguities would occur in a perfect associative memory if at least two messages would be identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.

@@

	\subsubsection{Simulations}
		Theoretical and empirical densities match very closely, see Figure \ref{densiteth} %gap of theoretical density with density in simulations : under $1$ percent,
